---
title: "2013_shell_tables"
format: html
editor: visual
---

## Quarto: Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

# Built Food Environment Shell Tables

## 2013 NC Birth Cohort Demographics Table

```{r}
library(quarto)
library(DT)

source("O:/PRIV/IRBData/Birth_Outcomes/Food Environment/built_food_environment/code/4a_demographics_birth_summary_2013.R")

```

```{r table-output, results='asis'}
my_table <- data_summary_race
DT::datatable(my_table, options = list(pageLength = 15))
```

``` {2+2}
```

## 2013 NC Birth Cohort Exposure Characteristics

```{r}
3+3
```

## Univariate Associations between Outcomes and (1) Demographics and (2) Exposure Variables

```{r}
4+4
```

## 
